Ceph Parallel File System Evaluation Report

### 2013-11-07 conclusion.tex
add intro

%Ceph is built on the assumption that the underlying hardware components are
%unreliable, with little or no redundancy and failure detection capability.
%This assumption is not valid for high-end HPC centers like OLCF. We have
%disabled replication for pools, haven't measured and quantified processing
%overhead, and we do not know yet if this would be significant. Investigating
%this remains as a future work. 
In our early tests, we experienced large performance swings during different
runs, low read performance when transfer size is small, and I/O errors tend to
happen when system is under stress (more clients and large transfer sizes).
However, with systematic performance engineering and development efforts, we
have seen a steady improvement through different releases. As of now, the Ceph
system on our testbed is able to perform close to 80\% of raw hardware
capability at RADOS level and close to 70\% at file system level (after
accounting for journaling overheads) . 
%This is still no comparison to Lustre
%yet, but by no means a small feat for such a \textit{young} technology. It is,
%in fact, a very respectable level of performance.

>>>>

%Ceph is built on the assumption that the underlying hardware components are
%unreliable, with little or no redundancy and failure detection capability.
%This assumption is not valid for high-end HPC centers like OLCF. We have
%disabled replication for pools, haven't measured and quantified processing
%overhead, and we do not know yet if this would be significant. Investigating
%this remains as a future work. 
In our early tests, we experienced large performance swings during different
runs, low read performance when transfer size is small, and I/O errors tend to
happen when system is under stress (more clients and large transfer sizes).
However, with systematic performance engineering and development efforts, we
have seen a steady improvement through different releases. As of now, the Ceph
system on our testbed is able to perform close to 70\% of raw hardware
capability at RADOS level and close to 62\% at file system level (after
accounting for journaling overheads) . 
%This is still no comparison to Lustre
%yet, but by no means a small feat for such a \textit{young} technology. It is,
%in fact, a very respectable level of performance.

### 2013-11-07 introduction.tex
add intro

Oak Ridge Leadership Computing Facility (OLCF)\footnote{This research was
supported by, and used the resources of, the Oak Ridge Leadership Computing
Facility, located in the National Center for Computational Sciences at ORNL,
which is managed by UT Battelle, LLC for the U.S. DOE (under the contract No.
DE-AC05-00OR22725).} at Oak Ridge National Laboratory (ORNL) has a long history
of deploying and running very-large-scale high-performance computing (HPC)
systems. 
%The facility hosted
%the Jaguar supercomputer up until recently, which was upgraded to the Titan
%supercomputer. 
In order to satisfy the I/O demand of such supercomputers, OLCF
also hosts large-scale file and storage systems. Lustre has been OLCF's choice
as the distributed parallel file system.  
%The latest such
%large-scale file systems is Spider II\cite{spider2}.  Spider II, deployed in
%2013, is designed to operate at over 1 TB/s peak aggregate I/O throughput and
%has a 40 PB of raw disk capacity. As the scratch 
%file system for Titan, a leadership computing platform,
%Spider II emphasizes \textit{capability} over \textit{capacity}. 
However, we
recognize that there are a wide variety of scientific data and emerging
workloads with different performance and data access requirements (e.g., RESTful
interface, S3-like API, cloud solution integration) which might not be
efficiently serviced by Lustre. OLCF is constantly evaluating new and emerging
file and storage system technologies.

This paper presents our findings on block I/O and file system performance of
Ceph for scientific high-performance computing (HPC) environments. Through
systematic experiments and tuning efforts, we observed that Ceph can perform
close to 80\% of raw hardware bandwidth at object level and close to 70\% of
at file system level. We also identified that Ceph's metadata plus data
journaling design is a weak spot as far as our particular storage
infrastructure is concerned.

>>>>

Oak Ridge Leadership Computing Facility (OLCF)\footnote{This research was
supported by, and used the resources of, the Oak Ridge Leadership Computing
Facility, located in the National Center for Computational Sciences at ORNL,
which is managed by UT Battelle, LLC for the U.S. DOE (under the contract No.
DE-AC05-00OR22725).} at Oak Ridge National Laboratory (ORNL) has a long history
of deploying and running very-large-scale high-performance computing (HPC)
systems. 
%The facility hosted
%the Jaguar supercomputer up until recently, which was upgraded to the Titan
%supercomputer. 
In order to satisfy the I/O demand of such supercomputers, OLCF
also hosts large-scale file and storage systems. Lustre has been OLCF's choice
as the distributed parallel file system for scratch I/O. 
%The latest such
%large-scale file systems is Spider II\cite{spider2}.  Spider II, deployed in
%2013, is designed to operate at over 1 TB/s peak aggregate I/O throughput and
%has a 40 PB of raw disk capacity. As the scratch 
%file system for Titan, a leadership computing platform,
%Spider II emphasizes \textit{capability} over \textit{capacity}. 
However, we
recognize that there are a wide variety of scientific 
%data and 
%emerging
workloads with different performance and data access requirements (e.g., RESTful
interface, S3-like API, cloud solution integration) which might not be
efficiently serviced by Lustre. 
%OLCF is constantly evaluating new and emerging
%file and storage system technologies.

%\textit{FEIYI: Are the 80\% and 70\% numbers still valid?}
This paper presents our evaluation and findings on block I/O and file system
performance of Ceph for scientific HPC environments. Through systematic
experiments and tuning efforts, we observed that Ceph can perform close to
70\% of raw hardware bandwidth at object level and about 62\% of at file
system level. We also identified that Ceph's metadata plus data journaling
design is currently a weak spot as far as our particular storage
infrastructure is concerned.
